Nature Index product

### 2023-09-04 DRAFT_nature_index.Rmd
Added references

---
title: "Nature Index product"
output:
  html_document
---

@@

The methodology for calculating NI is well established and has been described in  detail in NINA reports 347, 425, 426, 797, 1130, and 1886 (https://www.nina.no/Publikasjoner/NINA-Rapport) and several international scientific articles (e.g. https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0018930) and will not be elaborated on further here.

>>>>

---
title: "Nature Index product"
output:
  html_document
bibliography: book.bib
---

@@

The methodology for calculating NI is well established and has been described in  detail in NINA reports 347 [@nybo2008a], 425 [@nybo2008b], 797 [@pedersen2012], 1130 [@pedersen2015], and 1886 [@jakobsson2020] and several international scientific articles [e.g. @certain2011] and will not be elaborated on further here.
